---
title: "First SparkR Notebook"
output: html_notebook
---
This small example is taken almost verbatim from [sparklyr — R interface for Apache Spark](http://spark.rstudio.com).

Begin by loading the library and ensure Spark version 1.6.1 is installed

```{r}
library(dplyr)
library(sparklyr)
spark_install(version = "1.6.1")
```

Create a Spark context

```{r}
sc <- spark_connect(master = "local")
```

This Spark instance can be monitored in the Spark tab. So, let's load some data

```{r}
iris_tbl <- copy_to(sc, iris)
flights_tbl <- copy_to(sc, nycflights13::flights, "flights")
batting_tbl <- copy_to(sc, Lahman::Batting, "batting")
```

List all the tables in the Spark context
```{r}
src_tbls(sc)
```

Now, chose all flights that were delayed 2 (hours?) in departure
```{r}
flights_tbl %>% filter(dep_delay == 2)
```

Well, let's make a graphic that shows a delay and distance. First create the data set to visualise
```{r}
delay <- flights_tbl %>% 
   group_by(tailnum) %>% 
   summarise(count = n(), dist = mean(distance), delay = mean(arr_delay)) %>% 
   filter(count > 20, dist < 2000, !is.na(delay)) %>% 
   collect
```

and create the plot
```{r}
library(ggplot2)

ggplot(delay, aes(dist, delay)) +
   geom_point(aes(size = count), alpha = 1/2) +
   geom_smooth() +
   scale_size_area(max_size = 2)
```

